---
title: "Final Project"
author: "Tan Chin hong"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
---
# Abstract

In this work, we will use GARCH model (and its families) to forecast volatilities and use it on a financial risk measures which then be used for portfolio optimization problem.

```{r}
source("Utils.R")
```

# Dataset
```{r}
#df1 = read.csv("stocks_adj_prices1.csv")[1:504,]
df2 = read.csv("stocks_adj_prices2.csv")[1:753,]
stock_df = df2
```



The stock prioces given below is the adjusted prices
```{r}
require(zoo)
require(forecast)



head(stock_df)
tail(stock_df)
#View(stock_df)
#unique(is.na.data.frame(stock_df)) #no NA

rownames(stock_df)<-as.Date(stock_df[,1]);stock_df<-stock_df[,-1]
stock_df = zoo(stock_df, order.by = rownames(stock_df))





```



```{r}



stock_df_train<-train_test(stock_df)$train
stock_df_test<-train_test(stock_df)$test



```




For simplicity, we first consider one stock. We will generalize further into multiple stocks
# EDA



## Basic EDA

```{r, fig.height = 6}
basic_eda(stock_df[,1], lag = 52, cutoff = which(
           index(stock_df)>= as.Date("2024-01-01")
           )[1]
          ,x_1 = 300, y_1 = 200,
          x_2 = 600, y_2 = 140)
```


### using log_returns
```{r}


aapl_return_train<- calculate_returns(as.zoo(aapl_train), "log")
colnames(aapl_return_train)<- "AAPL"
```

```{r}
ts.plot(aapl_return_train)
```
```{r}
hist((aapl_return_train$AAPL), breaks = 30)
```
```{r}
require(zoo)
plot(stl(ts(aapl_return_train$AAPL, frequency = 252), s.window = "periodic"))

```

```{r}
if (!requireNamespace("fBasics", quietly = TRUE)) install.packages("fBasics")
library(fBasics)

basic_stats <- basicStats(aapl_return_train)
print(basic_stats[c("Mean", "Variance", "Skewness", "Kurtosis"), ])
```

### stationarity test
```{r}
#install.packages("aTSA")
require(aTSA)
```
```{r}
adf.test(as.matrix(aapl_return_train), nlag = 12)
```

The returns is stationary


```{r}
kpss.test(as.matrix(aapl_return_train))
```


The returns is stationary


### ARMA-GARCH modelling
```{r, warning=FALSE, fig.height=7}
par(mfrow = c(2,1))

acf(aapl_return_train, lag = 52);pacf(aapl_return_train, lag = 52)
```

```{r, warning=FALSE, fig.height=7}
par(mfrow = c(2,1))

acf(ts(aapl_return_train)^2, lag = 52);pacf(ts(aapl_return_train)^2, lag = 52)

```









```{r, fig.height=6, fig.width = 6}
library(FinTS)

archtest_lags <- list()

for (i in 1:12) {
  archtest_lags[[i]] <- ArchTest(arima(aapl_return_train, order = c(0,0,0), include.mean = FALSE)$residuals, lags = i)
}

# Extract lags, statistics, and p-values
arch_df <- data.frame(
  Lag = 1:12,
  Statistic = sapply(archtest_lags, function(x) x$statistic),
  P_Value = sapply(archtest_lags, function(x) round(x$p.value, 4))
)

# View the result
print(arch_df)

```
Indicating we need GARCH model

We use GARCH(1,1) with ARMA model order determined using AIC/BIC criterion
But first we check under ARMA(0,0)

```{r}
library(rugarch)
```



```{r}
spec <- ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(0, 0), include.mean = TRUE),
  distribution.model = "norm"
)

```



```{r}
fit_aapl_train<-ugarchfit(spec,aapl_return_train)
fit_aapl_train
```
We will find ARMA order of Garch 1-1
```{r}

aapl_models = list()
info_crit_aapl_train =list()
i=1
for (p in 0:4){
  for (q in 0:4){
        spec <- ugarchspec(
      variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
      mean.model = list(armaOrder = c(p, q), include.mean = TRUE),
      distribution.model = "norm")
        
        fit<-ugarchfit(spec,aapl_return_train)
        aapl_models[[paste0("ARMA ",p, ",", q)]]<-fit
        info_crit_aapl_train[[paste0("ARMA ",p, ",", q)]]<-infocriteria(fit)
        i = i+1  
  }
}


```

```{r}
# Assuming your list is named aic_list
ic_df_aapl_train <- do.call(rbind, lapply(names(info_crit_aapl_train), function(name) {
  data.frame(Model = name, t(as.data.frame(info_crit_aapl_train[[name]])))
}))

rownames(ic_df_aapl_train)<-ic_df_aapl_train$Model

# View result
round(ic_df_aapl_train[,-1],3)

```
```{r}
library(ggplot2)
library(tidyr)
aic_long <- pivot_longer(ic_df_aapl_train, cols = -Model, names_to = "Criterion", values_to = "Value")
ggplot(aic_long, aes(x = Model, y = Value, color = Criterion, group = Criterion)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  theme_minimal() +
  labs(title = "Information Criteria for ARMA Models",
       x = "Model",
       y = "Criterion Value") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```

Our final model is (3,0,3)(1,1)

```{r}
spec <- ugarchspec(
  variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
  mean.model = list(armaOrder = c(3, 3), include.mean = TRUE),
  distribution.model = "norm"
)

```



```{r}
fit_aapl_train<-ugarchfit(spec,aapl_return_train)
fit_aapl_train
```

```{r, fig.width=12, fig.height=9}
plot(fit_aapl_train, which = "all")

```


```{r}
plot(sigma(fit_aapl_train))
```


